Supplementary material for ``Screening Sinkhorn Algorithm for Regularized Optimal Transport''

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update suppl

Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.

>>>>

Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Screenkorn} problem.
Analysis of the quality of the subspace have been deported to the supplementary material (see Figure 1), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.
